Introducing statistics with \texttt{intRo}

### 2015-11-23 jcgs-paper-2016/paper.Rmd
Blurb on intRo package

TODO: Settle on licensing for intRo

The widespread adoption of \texttt{R} as a tool for statistical analysis has undoubtedly beenan important development for the scientific community. However, using \texttt{R} in most cases still requires a basic knowledge of programming concepts which may be unfamiliar to the introductory statistics student. This issue may explain why introductory courses often utilize software applications such as \texttt{JMP}, even though instructors would tend to use a tool like \texttt{R} in their own work. Still, signficant compromises must be made when using software like \texttt{JMP}, including dealing with software licenses, unsupported desktop platforms, and non-ideal user interface decisions.

@@

TODO: Talk about the package (briefly)

\texttt{intRo} is a web-based tool to accompany an introductory statistics class. It is meant to assist in the learning of statistics rather than a stand-alone deliverer of statistics education, with the intention of being used in conjunction with a guided class.

>>>>

The widespread adoption of \texttt{R} as a tool for statistical analysis has undoubtedly been an important development for the scientific community. However, using \texttt{R} in most cases still requires a basic knowledge of programming concepts which may be unfamiliar to the introductory statistics student. This issue may explain why introductory courses often utilize software applications such as \texttt{JMP}, even though instructors would tend to use a tool like \texttt{R} in their own work. Still, signficant compromises must be made when using software like \texttt{JMP}, including dealing with software licenses, unsupported desktop platforms, and non-ideal user interface decisions.

@@

\texttt{intRo} is a web-based tool to accompany an introductory statistics class. It is meant to assist in the learning of statistics rather than a stand-alone deliverer of statistics education, with the intention of being used in conjunction with a guided class. An accompanying R package, titled \texttt{intRo} and available on GitHub, assists in the downloading, running, and deploying of \texttt{intRo} instances.
